Forecasting the black Sigatoka development rate:\\ A comparison of machine learning techniques

### 2016-07-12 methodology.tex
Typos fixed
Methodology 12-julio

The data used for the current study was acquired in two research farms
of Corbana in Costa Rica%
%
\footnote{Both farms were also use in the study of \citet{Romero1995}.  Back
  then, \emph{La Rita} was referred to as \emph{Waldeck}.}
%
: \emph{28 Millas} located in the region of Matina, and \emph{La Rita}
located in Pococí, both in the province of Limón, Costa Rica.
%
Both farms produce banana fruit \emph{Musa} sp.\ AAA group 'Grande
Naine' (Cavendish subgroup).

The available input and output variables are summarized in
\tabref{tab:variables}.
%
\begin{table}[h] 
\centering
\begin{tabular}{l|l|c} 
\hline
\textbf{Symbol}  & \textbf{Description} & \textbf{Units} \\ 
\hline\hline 
$T_{a_{max}}$       & Maximal air temperature & $[^\circ$C$]$ \\
$T_{a_{min}}$       & Minimal air temperature & $[^\circ$C$]$ \\
$\overline{T}_{a}$ & Mean air temperature    & $[^\circ$C$]$ \\
$\overline{H}$    & Mean humidity           & ???  \\
$H_{min}$          & Minimal humidity        & ???  \\
$H_{max}$          & Maximal humidity        & ???  \\
$\overline{R}$    & Mean solar radiation    & $[$W/m$^2$$]$ \\
$P$               & Sum precipitation       & ??? \\
$W_{max}$          & Maximal wind speed      & $[$km/h$]$ \\
$\overline{W}$    & Mean speed wind         & $[$km/h$]$ \\
$L_2$             & Biological warning system – Leaf 2 & ???\\
$L_3$             & Biological warning system – Leaf 3 & ???\\
$L_4$             & Biological warning system – Leaf 4 & ???\\
\hline
$E_s$             & Biological warning system – Evolution Stage  & ???\\
\hline
\end{tabular} 
\caption{Variables available for the learning algorithms} 
\label{tab:variables} 
\end{table}

@@

The value to be predicted in all cases is the evolution stage $E_s$,
which corresponds to the total measure of the biological warning
system.

>>>>

The data used for the current study was acquired in two research farms
of Corbana in Costa Rica%
%
\footnote{Both farms were also use in the study of \citet{Romero1995}.  Back
  then, \emph{La Rita} was referred to as \emph{Waldeck}.}
%
: \emph{28 Millas} located in the region of Matina, and \emph{La Rita}
located in Pococí, both in the province of Limón, Costa Rica.
%
Both farms produce banana fruit \emph{Musa} sp.\ AAA group `Grande
Naine' (Cavendish subgroup).

The available input and output variables are summarized in
\tabref{tab:variables}.
%
\begin{table}[h] 
\centering
\begin{tabular}{l|l|c} 
\hline
\textbf{Symbol}  & \textbf{Description} & \textbf{Units} \\ 
\hline\hline 
$T_{a_{max}}$       & Maximal air temperature & $[^\circ$C$]$ \\
$T_{a_{min}}$       & Minimal air temperature & $[^\circ$C$]$ \\
$\overline{T}_{a}$ & Mean air temperature    & $[^\circ$C$]$ \\
$\overline{H}$    & Mean relative humidity           & $[0 - 100]$   \\
$H_{min}$          & Minimal relative humidity        & $[0 - 100]$  \\
$H_{max}$          & Maximal relative humidity        & $[0 - 100]$  \\
$\overline{R}$    & Mean solar radiation    & $[W/m^2]$ \\
$P$               & Precipitation       & $[mm]$ \\
$W_{max}$          & Maximal wind speed      & $[m/s]$ \\
$\overline{W}$    & Mean speed wind         & $[m/s]$ \\
\hline
$E_s$             & Biological warning system – Evolution Stage  & $>0$\\
\hline
\end{tabular} 
\caption{Variables available for the learning algorithms} 
\label{tab:variables} 
\end{table}

@@

The value to be predicted in all cases is the evolution stage $E_s$,
which is a measure of the level of disease progression.
